---
title: "2023 GOA BTS Otolith Collection Results"
author: "Zack Oyafuso (zack.oyafuso@noaa.gov); Ned Laman (ned.laman@noaa.gov); Ceclia O'Leary (cecelia.oleary@noaa.gov)"
date: "25 September 2023"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi Sandra and Chris,

Ned, Cecelia, and I negotiated the otolith requests with Kalei, Sandra, Paul, Jane, Meaghan, Carey, Ingrid, and Cole for their respective stocks for the 2023 Gulf of Alaska bottom trawl survey. This is a table of the total otolith pair requested versus collected across the 16 species that were requested.

```{r, echo = F, include = F}
library(knitr)
observed_collection <- readRDS("observed_otoliths.RDS")
requests <- read.csv(file = "goa_2023_otolith_requests.csv")

observed_collection <- merge(x = observed_collection, by.x = "common_name",
                             y = requests, by.y = "species_name")

```

```{r, echo = F}
results <- observed_collection[, c("common_name", "total_requested", "freq")]
results$diff <- results$freq - results$total_requested
results$perc_diff <- round(x = 100 * results$diff / results$total_requested)

# AI_report <- read.csv(file = "../reports/202201_AI_otolith.csv")
# knitr::kable(AI_report, 
#              align = c("c", "l", "l", "c", "c", "l"), 
#              col.names = c("Species Code", "Species Name", "Common Name", 
#                            "Total Requested", "Total Collected", "Notes"))
```


Twelve of the 16 species' otolith targets were met or within 10%. Four species 
were under: Greenland turbot and shortraker, harlequin, and rougheye rockfish. 
For these four species, the total number of individuals observed (caught) were 
much less than the total number of otoliths collected (see below). 

```{r, echo = F, message = F}
# under_lens <- readRDS("../reports/under_lens.rds")
# idx <- match(names(under_lens), AI_report$species_code)
# kable(data.frame("Species Code" = AI_report$species_code[idx],
#                  "Common Name" = AI_report$common_name[idx],
#                  "Total Otoliths Requested" = AI_report$total_requested[idx],
#                  "Total Individuals Observed" = as.numeric(under_lens),
#                  "Total Otoliths Collected" = AI_report$total_collected[idx],
#                  check.names = F),
#       align = c("c", "l", "c", "c", "c"))
```

Five Greenland turbot and two harelquin rockfish that could have been 
collected were missed by accident. Eight rougheye rockfish and 97 shortraker 
rockfish were not collected because of the collection rule (maximum 10 and 12 
random/haul, respectively).
